### 2024-09-17 cognitive-bias.qmd
20240916 - risk aversion bias

- [overconfidence bias](#sec-cognitiveBiasesOverconfidence)
- [optimism bias](#sec-cognitiveBiasesOptimism)
- [confirmation bias](#sec-cognitiveBiasesConfirmation)
- [in-group bias](#sec-cognitiveBiasesInGroup)
- [hindsight bias](#sec-cognitiveBiasesHindsight)
- [outcome bias](#sec-cognitiveBiasesOutcome)
- [self-serving bias](#sec-cognitiveBiasesSelfServing)
- [omission bias](#sec-cognitiveBiasesOmission)
- [loss aversion bias](#sec-cognitiveBiasesLossAversion)
- [primacy effect bias](#sec-cognitiveBiasesPrimacy)
- [recency effect bias](#sec-cognitiveBiasesRecency)
- [framing effect bias](#sec-cognitiveBiasesFraming)
- [endowment effect bias](#sec-cognitiveBiasesEndowment)
- [bandwagon effect bias](#sec-cognitiveBiasesBandwagon)
- [Dunning–Kruger effect bias](#sec-cognitiveBiasesDunningKruger)

@@

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is different from risk aversion.
Risk aversion is the tendency to prefer outcomes with low uncertainty (compared to outcomes with greater uncertainty).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto underperforming high drafts for too long instead of a starting a more promising player out of fear of losing potential value from their initial investment.

@@

Note how information is framed, knowing that the framing itself could lead you astray.
Thus, try to focus on the information itself rather than the framing when making decisions.

>>>>

- [overconfidence bias](#sec-cognitiveBiasesOverconfidence)
- [optimism bias](#sec-cognitiveBiasesOptimism)
- [confirmation bias](#sec-cognitiveBiasesConfirmation)
- [in-group bias](#sec-cognitiveBiasesInGroup)
- [hindsight bias](#sec-cognitiveBiasesHindsight)
- [outcome bias](#sec-cognitiveBiasesOutcome)
- [self-serving bias](#sec-cognitiveBiasesSelfServing)
- [omission bias](#sec-cognitiveBiasesOmission)
- [loss aversion bias](#sec-cognitiveBiasesLossAversion)
- [risk aversion bias](#sec-cognitiveBiasesRiskAversion)
- [primacy effect bias](#sec-cognitiveBiasesPrimacy)
- [recency effect bias](#sec-cognitiveBiasesRecency)
- [framing effect bias](#sec-cognitiveBiasesFraming)
- [endowment effect bias](#sec-cognitiveBiasesEndowment)
- [bandwagon effect bias](#sec-cognitiveBiasesBandwagon)
- [Dunning–Kruger effect bias](#sec-cognitiveBiasesDunningKruger)

@@

*Loss aversion bias* is the tendency to avoid losses rather than acquiring equivalent gains.
That is, loss aversion (similar to punishment sensitivity, as opposed to reward sensitivity) is the tendency to weigh losses (or punishment) more heavily than gains (or rewards).
Loss aversion is different from [risk aversion](#sec-cognitiveBiasesRiskAversion).
Loss aversion is exemplified when teams play conservatively so as "not to lose" instead of "to win."
In fantasy football, loss aversion may lead managers to start or hold onto underperforming high drafts for too long instead of a starting a more promising player out of fear of losing potential value from their initial investment.

### Risk Aversion Bias {#sec-cognitiveBiasesRiskAversion}

Risk aversion is the tendency to prefer outcomes with low uncertainty (compared to outcomes with greater uncertainty).
For instance, a fantasy manager may prefer to draft players who have demonstrated performance compared to players right out of college with no proven history in the NFL.

Risk seeking, by contrast, has been observed in entrepreneurs and in generals when all of their options are poor [@Kahneman2011].
In fantasy football, risk seeking may be more likely when a manager has a team full of underperforming players.

@@

Pay attention to how information is framed, knowing that the framing itself could lead you astray.
Thus, try to focus on the information itself rather than the framing when making decisions.
